### 2019-08-02 reports/thesis/book.tex
Started writing on noContamination experiment
tex: made command /addNumber which inputs a text file protected and without space at the end
.eps figures are saved in allNullGaussian
.txt files are saved in allNullGaussian
new figures in allNullGaussian
Writing up allnull experiments
Wrote subsection No Contamination Experiment, Contamination Experiment
Experiment_AllNull export numbers and figures
inputNumber command in latex
Appendix for inference
Start literture review
Start chapter 2
printResults for GlmSelect
GlmSelect write up
Compound Poisson complete re-write
Histogram class
Re-wrote com

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots

@@

\newcommand{\RSS}{\mathrm{RSS}}
\newcommand{\euler}{\mathrm{e}}
\newcommand{\diff}{\mathrm{d}}
\newcommand{\T}{^\textup{T}}
\newcommand{\dotdotdot}{_{\phantom{.}\cdots}}
\newcommand{\BIC}{\textup{BIC}}

@@

@@

\includepdf{title.pdf}

\frontmatter
\section*{Abstract}
X-ray computed tomography (CT) can be used for defect detection in 3D printing. The object is scanned at multiple angles to reconstruct the object in 3D space. The process can be time consuming. The aim of this project was to investigate if it is possible to conduct defect detection in projection space from a single scan to speed up the defect detection procedure. To do this, a 3D printed sample was manufactured with voids to see if they can be detected.

@@

\section*{Acknowledgements}
\begin{itemize}
	\item Supervisors: Julia Brettschneider and Tom Nichols
	\item Inside Out Team: Wilfrid Kendall, Audrey Kueh, Jay Warnett and Clair Barnes
	\item EPSRC Funding: EP/L016710/1
\end{itemize}

\newpage
\tableofcontents*

@@

\chapter{Data Collection}

@@

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements
\usepackage{rotating}
\usepackage{multirow} %for multirow tables
\usepackage{mathtools} %multlined
\usepackage{longtable}

@@

\newcommand{\RSS}{\mathrm{RSS}}
\newcommand{\euler}{\mathrm{e}}
\newcommand{\diff}{\mathrm{d}}
\newcommand{\T}{^\textup{T}}
\newcommand{\dotdotdot}{_{\phantom{.}\cdots}}
\newcommand{\BIC}{\mathrm{BIC}}
\newcommand{\AIC}{\mathrm{AIC}}

\newcommand{\subSize}{0.49\textwidth}
\newcommand{\mainSize}{0.8\textwidth}

@@

\newcommand{\addNumber}[1]{\protect\input{#1}\unskip}
\newcommand{\inputNumber}[1]{\protect\input{#1}\unskip}

\DeclareSIUnit\pixel{px}
\DeclareSIUnit\adu{ADU}

@@

\begin{titlingpage}
\centering
{\LARGE Characterisation of Computed Tomography Noise in Projection Space with Applications in Additive Manufacturing \par}
\vspace{1cm}
{\Large Sherman E.~Lo\par}
{\Large Doctor of Philosophy in Statistics\par}
\vfill
{\Large University of Warwick\par}
{\Large Department of Statistics\par}
{\Large September 2019\par}
\end{titlingpage}

\frontmatter

\newpage
\tableofcontents*
\newpage
\listoffigures
\newpage
\listoftables

\chapter{Acknowledgements}
I would like to thank my supervisors Julia Brettschneider and Tom Nichols. I would also like to thank my calibrators, as part of the Inside-Out group, in Warwick Statistics, Clair Barnes, Wilfred Kendall and Audrey Kueh, and the Warwick Manufacturing Group, Greg Gibbons, Jay Warnett and Mark Williams.

This work is funded by the EPSRC and MRC Centre for Doctoral Training in Next Generation Statistical Science: The Oxford-Warwick Statistics Programme (EP/L016710/1). I would like to thank my cohort for the friendship and collaboration during the programme: Nathan Cunningham, Giuseppe di Benedetto, Beniamino Hadj-Amar, Jack Jewson, Ella Kaye, Leon Law, Kaspar Martens, Marcin Mider, Xenia Miscouridou, Paul Vanetti and Andi Wang.

\chapter{Declaration}
This thesis is the author's own work and has not been published at the time of submitting.

This thesis is a result of collaborative research with Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing funded by EPSRC (EP/K031066/1).  Greg Gibbons and Jay Warnett, from the Warwick Manufacturing Group, were responsible for the fabrication, x-ray computed tomography acquisition and simulation of test samples used in this thesis. In this thesis, they are referred to as engineers.

This thesis has not been submitted for a degree at another university.

\chapter{Abstract}
X-ray computed tomography (CT) can be used for defect detection in 3D printing. The object is scanned at multiple angles to reconstruct the object in 3D space. The process can be time consuming. The aim of this project was to investigate if it is possible to conduct defect detection in projection space from a single scan to speed up the defect detection procedure. To do this, a 3D printed sample was manufactured with voids to see if they can be detected.

@@

@@

\chapter{Data Collection}
\input{chapters/2_dataCollection.tex}

@@

\begin{appendices}
\input{chapters/appendix.tex}
\end{appendices}
